Who does big team science?

### 2024-09-11 manuscript_definition.Rmd
updating with outline

@@

## RQ1

@@

>>>>

outline:

- what is team science / collaboration 
- research on how it's grown / changed over time? 
- Any research diversification?
  - on who is publishing 
  - on where is represented 
- "big" teams - unanswered question ... people are now using term "big team" but it's not defined - can we define it and see if it's any different or just a product of growth/internet over time?

@@

## RQ1 change over time

@@

updated binning:

- teams: 2-10 authors, 2-5 inst
  - first and last author only versus everyone else
- big ass teams: 6+ affs
  - small: 11-49
    - first three plus last versus everyone else
  - medium: 50-99
    - first five plus last versus everyone else
  - large: 100+
    - first 10 plus last versus everyone else

for time:
 teams versus big teams combining results
 separate panel of the big teams separated (not by time)
